### 2014-03-08 docs/related-work.tex
Note on similarity with Telex.

>>>>

Of the decoy routing systems, Telex is the most similar to ours.
Both use a piece of network infrastructure as a decoy to redirect certain flows
(for Telex it is an ISP router; for us it is the Google frontend server),
and both tag flows in a way that is visible only to the decoy
(for Telex a tag is a hash embedded in the TLS client randomness; for us it is the HTTP Host header).
